A Multi-Modal Model of Object Deformation under Robotic Pushing

### 2017-01-25 twostagedo-rev-final.tex
Constraints... 2

\subsubsection{Preservation of Angles}
The previous terms can not do anything to restore the mesh if triangles get flipped during deformation, which is not a valid state since the mesh models the surface of a 3D object.  For this reason we included a new term that enforces the preservation of the original angles of the triangles.  [\fref{fig:forces}(c)] gives an idea of how these forces look.  Here the energy depends on the difference between the current angle, between adjacent edges, and the angle between them at the equilibrium position. The constraint for this potential energy is given by\footnote{It was also considered to multiply $E_\varphi$ by the lengths of the edges, but it hasn't improved the performance of the model.}:
\begin{align}
 %E_\varphi(\varphi) & = \frac{1}{2}k_\varphi(\varphi - \varphi_0)^2 \\
 C &= \varphi - \varphi_0 \\
 \varphi(p_i,p_j,p_k) & = \arccos \left( \dfrac{(p_j - p_i) \cdot (p_k - p_i)}{ \left\| p_j - p_i \right\| \left\|p_k - p_i \right\|} \right)^2 \nonumber
\end{align}
where $\varphi$ is the angle between adjacent edges,% $E_\varphi$ is the energy associated with changes in the angle, $k_\varphi$ is the corresponding stiffness constant, 
and the $p_i$s are the Cartesian coordinates of the mass particles.

>>>>

\subsubsection{Preservation of Angles}
The previous terms can not do anything to restore the mesh if triangles get flipped during deformation, which is not a valid state since the mesh models the surface of a 3D object.  For this reason we included a new term that enforces the preservation of the original angles of the triangles.  [\fref{fig:forces}(c)] gives an idea of how these forces look.  Here the energy depends on the difference between the current angle, between adjacent edges, and the angle between them at the equilibrium position. The constraint for this potential energy is given by\footnote{It was also considered to multiply $E_\varphi$ by the lengths of the edges, but it hasn't improved the performance of the model.}:
\begin{align}
 %E_\varphi(\varphi) & = \frac{1}{2}k_\varphi(\varphi - \varphi_0)^2 \\
 C &= \varphi - \varphi_0 \\
 \varphi(p_i,p_j,p_k) & = \arccos \left( \dfrac{(p_j - p_i) \cdot (p_k - p_i)}{ \left\| p_j - p_i \right\| \left\|p_k - p_i \right\|} \right)^2 \nonumber
\end{align}
where $\varphi$ is the angle between adjacent edges, and $\varphi_0$ is the angle at rest.  % $E_\varphi$ is the energy associated with changes in the angle, $k_\varphi$ is the corresponding stiffness constant, 
%and the $p_i$s are the Cartesian coordinates of the mass particles.
